Comparison of Catalogs

### 2024-07-25 compare/compare.qmd
Heatmaps and pairgrids

---
title: "Comparison of Catalogs"
format: html
toc: true
toc-depth: 2
theme: minti
bibliography: ../My_Library.bib
execute: 
  echo: true
  eval: true
---

@@

@@

|  LCV  | HECATE |   Description   | Pearson Correlation \[-1,1\] |
|:-----:|:------:|:---------------:|:----------------------------:|
| Ra_1  |  RA_2  | Right Ascension |      `{python} ra_corr`      |
| Dec_1 | DEC_2  |   Declination   |     `{python} dec_corr`      |
|  Dis  |   D    |    Distance     |      `{python} d_corr`       |
::: panel-tabset
## Right Ascnsion
```{python}

scatter_plot(dt["Ra_1"], dt["RA_2"])
```
## Declination
```{python}
scatter_plot(dt["Dec_1"], dt["DEC_2"]), 
```
## Distance
```{python}
scatter_plot(dt["Dis"], dt["D"])
```
:::
## Velocities

@@

|       LCV        |        HECATE         |         Description          |        Linear Correlation         |
|:----------------:|:-----------------:|:----------------:|:----------------:|
|       RVel       | V/V_VIR (with errors) | Heliocentric radial velocity | `{python} rvel_corr, rvel_corr_v` |
|       VLG        | V/V_VIR (with errors) |       Radial velocity        |  `{python} vlg_corr, vlg_corr_v`  |
| cz (with errors) | V/V_VIR (with errors) |    Heliocentric velocity     |   `{python} cz_corr, cz_corr_v`   |

@@

@@

As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0

@@

scatter_plot(dt["TType"], dt["T"], yerr = dt["E_T"])
scatter_plot(dt["inc"], dt["INCL"], sigma =True)
scatter_plot(dt["a26_1"], dt["R1"])

@@

```{python}
scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma = True)
scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"], sigma = True)
```

## Absorbsion

@@

```{python}
#| echo: false
sfr_data.drop("logSFR_GSW", axis=1, inplace=True)
# Compute the correlation matrix
corr_matrix = sfr_data.corr()

# Create a heatmap
plt.figure(figsize=(10, 8))
sns.heatmap(corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of SFR Values")
plt.show()

# Create a pair grid
sns.pairplot(sfr_data)
plt.show()

It is possible we dont see a correlation because we dont have a big enough common sample

@@

::: panel-tabset
## Heatmap
```{python}
mass_data.drop("logM_GSW", axis=1, inplace=True)
# Compute the correlation matrix
mass_corr_matrix = mass_data.corr()

# Create a heatmap
sns.heatmap(mass_corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of Mass Values")
plt.show()
```
## Plot Grid
```{python}
# Create a pair grid
sns.pairplot(mass_data)
plt.show()
```
:::

>>>>

---
title: "Comparison of Catalogs"
format: html
toc: true
toc-depth: 2
theme: minti
bibliography: ../My_Library.bib
execute: 
  echo: false
  eval: true
---

@@

Some data seem to have a very good linear correlation but they have many outliers. This is why we will clip the outliers whith $sigma > 3$

@@

|  LCV  | HECATE |   Description   | Pearson Correlation \[-1,1\] |
|:-----:|:------:|:---------------:|:----------------------------:|
| Ra_1  |  RA_2  | Right Ascension |      `{python} ra_corr`      |
| Dec_1 | DEC_2  |   Declination   |     `{python} dec_corr`      |
|  Dis  |   D    |    Distance     |      `{python} d_corr`       |

::: panel-tabset
## Right Ascnsion

scatter_plot(dt["Ra_1"], dt["RA_2"])
```

## Declination

```{python}
scatter_plot(dt["Dec_1"], dt["DEC_2"]), 
```

## Distance

```{python}
scatter_plot(dt["Dis"], dt["D"])
```
:::

## Velocities

@@

|     LCV     |    HECATE    |              Description               |  Linear Correlation  |
|:----------------:|:-----------------:|:----------------:|:----------------:|
| RVel (km/s) |   V (km/s)   |      Heliocentric radial velocity      | `{python} rvel_corr` |
| VLG (km/s)  |              |            Radial velocity             |                      |
|  cz (km/s)  |              |         Heliocentric velocity          |                      |
|             | V_VIR (km/s) | Virgo-infall corrected radial velocity |                      |

::: panel-tabset
## Heliocentric radial Velocity

@@

## Scatter Grid
```{python}
vel_data = dt[["RVel", "V", "VLG", "cz", "V_VIR"]].to_pandas()

# Create a pair grid
sns.pairplot(vel_data, corner=True)
plt.show()
```

## Heatmap
```{python}
# Compute the correlation matrix
corr_matrix = vel_data.corr()

# Create a heatmap
plt.figure(figsize=(10, 8))
sns.heatmap(corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of Velocity Values")
plt.show()
```

:::

@@

::: panel-tabset
## Galaxy Types

@@

scatter_plot(dt["TType"], dt["T"], yerr = dt["E_T"])

```
As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0

## Inclanation
```{python}
scatter_plot(dt["inc"], dt["INCL"], sigma =True)
```
## Major Axis

```{python}
scatter_plot(dt["a26_1"], dt["R1"])
```

:::

@@

::: panel-tabset
# B mag
```{python}
scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma = True)
```

## K mag

scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"], sigma = True)
```
:::
## Absorbsion

@@

::: panel-tabset
## Heatmap
```{python}
#| echo: false
sfr_data.drop("logSFR_GSW", axis=1, inplace=True)
# Compute the correlation matrix
corr_matrix = sfr_data.corr()

# Create a heatmap
plt.figure(figsize=(10, 8))
sns.heatmap(corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of SFR Values")
plt.show()
```
## Scatter Grid
```{python}
# Create a pair grid 
sns.pairplot(sfr_data, corner=True)
plt.show()

```
:::
It is possible we dont see a good correlation because we dont have a big enough common sample

@@

::: panel-tabset
## Heatmap

```{python}
mass_data.drop("logM_GSW", axis=1, inplace=True)
# Compute the correlation matrix
mass_corr_matrix = mass_data.corr()

# Create a heatmap
sns.heatmap(mass_corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of Mass Values")
plt.show()
```

## Plot Grid

```{python}
# Create a pair grid
sns.pairplot(mass_data, corner=True)
plt.show()
```
:::
